\begin{publications}

% \bibitem... entries for each publication.
% The easiest way to feed this part is to cut/paste from a .bbl file
% Alternatively, here is an example:

{\large\textbf{Journal Publications}} \\
\begin{enumerate}

\item 
A.~Yao, J.~Gall, L.~Van~Gool.  Coupled Action Recognition and Pose Estimation
from Multiple Views.  {\em International Journal of Computer Vision (IJCV)},
2012.  100(1), 16-37.

\item 
J.~Gall, A.~Yao, N.~Razavi, L.~Van~Gool and V.~Lempitsky. Hough Forests for
Object Detection, Tracking and Action Recognition.  {\em IEEE Transactions on
Pattern Analysis and Machine Intelligence (PAMI)}, 2011.  33(11), 2188-2202.

\item
A.Y.J.~Yao and W.~Einhaeuser.  Colour aids late but not early stages of rapid
natural scene recognition.  {\em Journal of Vision}, 2008. 8(16):12, 1-13. \\
\end{enumerate}

{\large\textbf{Refereed Conference Proceedings}} \\
\begin{enumerate}
\item
A.~Yao, J.~Gall, C.~Leistner and L.~Van~Gool.  Interactive Object Detection. 
In {\em Proceedings IEEE Conference on Computer Vision
and Pattern Recognition (CVPR)}, 2012. 

\item
A.~Yao, J.~Gall, L.~Van Gool, and R.~Urtasun.  Learning Probabilistic Non-Linear
Latent Variable Models for Tracking Complex Activities.  {\em Neural
Information Processing Systems (NIPS)}, 2011.

\item
A.~Yao, J.~Gall, G.~Fanelli and L.~Van~Gool. Does Human Action
Recognition Benefit from Pose Estimation? In {\em Proceedings British Machine
Vision Conference (BMVC)}, 2011.

\item
A.~Yao, D.~Uebersax, J.~Gall and L.~Van~Gool.  Tracking People in Broadcast
Sports. In {\em Proceedings German Association for Pattern Recognition (DAGM)},
2010.

\item
J.~Gall, A.~Yao and L.~Van~Gool.  2D Action Recognition Serves 3D Human Pose
Estimation.  In {\em Proceedings European Conference on Computer Vision (ECCV)},
2010.

\item
A.~Yao, J.~Gall and L.~Van~Gool.  a Hough Transform-Based Voting Framework
for Action Recognition. In {\em Proceedings IEEE Conference on Computer Vision
and Pattern Recognition (CVPR)}, 2010. \\

\end{enumerate}

{\large\textbf{Others}} \\
\begin{enumerate}
\item 
D. Waltisberg, A.~Yao, J.~Gall and L.~Van~Gool.  Variations of a Hough-Voting
Action Recognition System.  {\em Proceedings International Conference on Pattern
Recognition (ICPR) Contests}, 2010.

\item
G.~Fanelli, A.~Yao, P.L.~Noel, J.~Gall and L.~Van~Gool.  Hough Forest-Based
Facial Expression Recognition from Video Sequences.  {\em International
Workshop on Sign, Gesture and Activity (SGA)},
2010.
\end{enumerate}

\end{publications}