
The complexity scales quadratically with the dimensionality of the
features. This pose a problem for real-time applications with limited
memory budget.


1. Once image features were extracted, the question remained as to how
they could be indexed and matched against each other for retrieval.

2. low-cost storage and easy web hosting has fueled the metamorphosis
of common man from a passive consumer of photography in the past to a
current-day active producer. Today, searchable image data exists with
extremely diverse visual and semantic content, spanning geographically
disparate locations, and is rapidly growing in size. All these factors
have created innumerable possibilities and hence considerations for
real-world image search system designers.

3.  some of the key motivating factors behind the design of the proposed image similarity measures can be summarized as follows: 
-- agreement with semantic --robustness to noise -- computational efficiency -- invariance to background -- local linearity 


4. The different distance measures discussed so far have their own
advantages and disadvantages. While simple methods lead to very
efficient computation, which in turn makes image ranking scalable (a
quality that greatly benefits real-world applications), they often are
not effective enough to be useful. 

5. Papers have flourished, and some have reported very good results on
challenging benchmarks, such as.... Moreover, papers sometimes lack
descriptions of critical details that are required to reproduce the
proposed methods, and do not discuss certain aspects such as memory
consumption and speed that are of critical importance in applicaiton. 


6. LLE illustrates a general principle of manifold learning,
elucidated by Martinetz and Schulten (20) and (4), that overlapping
local neighborhoods -- collectively analyzed -- can provide
information about global geometry ~\cite{lle:science:00}. 

7. expensive features: computationally, training, require an auxiliary
large labeled object database to train a deep convolutional
architecture.

8. To accelerate retrieval, dimension is reduced ....  

9. such a metri imitation can find immediate application in multiple places, and we mention two cases here.  

